\documentclass[draft]{trlnotes}
\usepackage{trmath}
\addcompatiblelayout{thesis}
\setlayout{thesis}

\setmainfont{PT Serif}
\setsansfont{Nunito Sans}[
   BoldFont    = {Nunito Sans Semibold}
]

\setmonofont{CMU Typewriter Text}
\newfontfamily\cyrillicfonttt{CMU Typewriter Text}[Script=Cyrillic]

\setmathfont{STIX Two Math}
% Use XITSMath for    [     ]     (     )     {     }
% \setmathfont[range={"005B,"005D,"0028,"0029,"007B,"007D}]{XITS Math}
% но не все, а только фигурные
\setmathfont[range={"007B,"007D,"023DF}]{XITS Math}


\usepackage{aas_macros}
\usepackage{trthm}
\usepackage{trphys}
\usepackage[normalem]{ulem}
\usepackage{trsym}
\usepackage{docmute}
\usepackage{luacode}
% \usepackage{tikz}
\usepackage[
  backend=biber,
  natbib=true,
  style=authoryear-comp,
  sorting=nyt,
  uniquename=false
]{biblatex}
\addbibresource{thesisrefs.bib}
% \tikzexternalize
% \tikzexternalize[prefix=figures-tikz/]
\begin{document}
\begin{otherlanguage}{english}
% \input{titlepage}\newpage
\input{titlepage_en_it} 

\begin{abstract}
According to the recent IR surveys, almost $2/3$ of all disk galaxies host
bars. At the same time, the bars in early type disk galaxies seen face-on can be
divided in at least two distinct groups: bars with the barlenses and face-on peanuts.
The principal objective of my work is to explain what is behind this difference
in face-on bar morphologies.

The distinctive feature of the bars with the barlenses is the lenticular thickening in the
center, constituting approximately half the length of the bar.
They were introduced in the literature by \citet{laurikainen2011}.
Despite the fact that the barlenses were studied in great detail, their
nature still remains unknown. The second bar type is the face-on peanut, characterized by box-like or peanut-like isophotes.
Both types manifest themselves in observations, numerous examples are provided by \citet{laurikainen2017}.
\citet{salo2017} have shown that it is possible to obtain
different bar morphologies in self-consistent N-body simulations.  This result
was confirmed by \citet{smirnov2018}.
Increasing concentration of the bulge in a model causes a transformation of the visible shape: 
from the face-on peanut to the bar with barlens.
However, to understand the physical reasons for this metamorphosis it is
crucially important to study the orbital structure of the models and to find
orbital families, responsible for the specific morphology.

In this work, we examine 4 N-body models of disk galaxies
with bars that show a smooth transition from the face-on peanut morphology to the bar with the
barlens. From the spectral analysis of individual orbits in the simulations,
we show that this diversity is due to different populations of orbital families
that are responsible for the observed features.  By classifying the specimens
from them in detail and providing the backbone orbits for each family we show
how the gradual increase of the bulge concentration in a model leads to the
domination of orbits that do not constitute the bar in its classical meaning
and form a roundish morphology over the box family supporting the face-on
peanut bar. 

\end{abstract}

\setcounter{page}{3}
\tableofcontents
\clearpage


\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction: bars and B/PS bulges}
% \input{tex/intro/intro.tex}

\chapter{Models}
\label{chap:model}
% \input{tex/model/model.tex}

\chapter{Analysis of dominant frequencies}
\label{chap:method}
% \input{tex/method/method.tex}

\chapter{Classification of orbital families}
\label{chap:split}
% \input{tex/families/split.tex}

\chapter{Orbital composition in detail}
\label{chap:orbits}
% \input{tex/families/orbits.tex}

\chapter{Discussion}
\label{chap:discuss}
% \input{tex/discuss/discussion.tex}

\chapter*{Conclusion}
\addcontentsline{toc}{chapter}{Conclusion}
\label{chap:conc}
% \input{tex/conc/conclusion.tex}
\clearpage

\appendix

%библиография есть, но на overleaf с ней не собирается
\printbibliography[
  heading=bibintoc,
  title={References}
]
\end{otherlanguage}
\end{document}

